A non-additive generalization of probability theory \\for quantum mechanics and beyond

### 2025-07-31 Articles/2024-NonAdditiveProbability/NonAdditiveProbability.tex
NonAdditiveProbability: minor changes to captions

		% meridians and equator
		\begin{scope}[canvas is yz plane at x=0]
			\draw (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, delta angle=180, radius=1 cm];
			\draw[dashed] (-\ixy, -\ixz) arc[start angle={atan2(-\ixz, -\ixy)}, delta angle=180, radius=1 cm];
		\end{scope}
		\begin{scope}[canvas is zx plane at y=0]
			\draw[dashed] (\iyz, \iyx) arc[start angle={atan2(\iyx, \iyz)}, delta angle=180, radius=1 cm];
			\draw (-\iyz, -\iyx) arc[start angle={atan2(-\iyx, -\iyz)}, delta angle=180, radius=1 cm];
		\end{scope}
		\begin{scope}[canvas is xy plane at z=0]
			\draw[dashed] (\izx, \izy) arc[start angle={atan2(\izy, \izx)}, delta angle=180, radius=1 cm];
			\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, delta angle=180, radius=1 cm];
		\end{scope}
	\end{tikzpicture}
	\caption{Examples of a classical (triangle) and quantum (ball) ensemble space in three and two dimensions, respectively.}
\end{figure}

@@

		% meridians and equator
		\begin{scope}[canvas is yz plane at x=0]
			% foreground above s
			\draw (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=90-\stheta, radius=1 cm] coordinate (C);
			% foreground below s
			\draw[dashed] (C) arc[start angle=90-\stheta, end angle={atan2(-\ixz, -\ixy)}, radius=1 cm] coordinate (D);
			% background below s
			\draw[loosely dotted] (D) arc[start angle={atan2(-\ixz, -\ixy)}, end angle=\stheta+270, radius=1 cm];
			% background above s
			\draw[densely dotted] (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=\stheta-90, radius=1 cm];
		\end{scope}
%		\begin{scope}[canvas is xy plane at z=0]
%			\draw[dashed] (\izx, \izy) arc[start angle={atan2(\izy, \izx)}, delta angle=180, radius=1 cm];
%			\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, delta angle=180, radius=1 cm];
%		\end{scope}
		\begin{scope}[canvas is xy plane at z=0]
			% foreground above s
			\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=180-\stheta, radius=1 cm] coordinate (E);
			% foreground below s
			\draw[dashed] (E) arc[start angle=180-\stheta, end angle={atan2(\izy, \izx)+360}, radius=1 cm] coordinate (F);
			% background below s
			\draw[loosely dotted] (F) arc[start angle={atan2(\izy, \izx)}, end angle=\stheta, radius=1 cm];
			% background above s
			\draw[densely dotted] (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=\stheta, radius=1 cm];
		\end{scope}
	\end{tikzpicture}
	\caption{Geometrical representation of the element $\ens[e]$ in $A(s)$ with the largest fraction of $\ens[o]$.}
\end{figure}

>>>>

		% meridians and equator
		\begin{scope}[canvas is yz plane at x=0]
			\draw (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, delta angle=180, radius=1 cm];
			\draw[dashed] (-\ixy, -\ixz) arc[start angle={atan2(-\ixz, -\ixy)}, delta angle=180, radius=1 cm];
		\end{scope}
		\begin{scope}[canvas is zx plane at y=0]
			\draw[dashed] (\iyz, \iyx) arc[start angle={atan2(\iyx, \iyz)}, delta angle=180, radius=1 cm];
			\draw (-\iyz, -\iyx) arc[start angle={atan2(-\iyx, -\iyz)}, delta angle=180, radius=1 cm];
		\end{scope}
		\begin{scope}[canvas is xy plane at z=0]
			\draw[dashed] (\izx, \izy) arc[start angle={atan2(\izy, \izx)}, delta angle=180, radius=1 cm];
			\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, delta angle=180, radius=1 cm];
		\end{scope}
	\end{tikzpicture}
	\caption{Examples of a classical discrete ensemble space with three pure states (triangle) and of a two dimensional quantum ensemble space (ball).}
\end{figure}

@@

		% meridians and equator
		\begin{scope}[canvas is yz plane at x=0]
			% foreground above s
			\draw (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=90-\stheta, radius=1 cm] coordinate (C);
			% foreground below s
			\draw[dashed] (C) arc[start angle=90-\stheta, end angle={atan2(-\ixz, -\ixy)}, radius=1 cm] coordinate (D);
			% background below s
			\draw[loosely dotted] (D) arc[start angle={atan2(-\ixz, -\ixy)}, end angle=\stheta+270, radius=1 cm];
			% background above s
			\draw[densely dotted] (\ixy, \ixz) arc[start angle={atan2(\ixz, \ixy)}, end angle=\stheta-90, radius=1 cm];
		\end{scope}
%		\begin{scope}[canvas is xy plane at z=0]
%			\draw[dashed] (\izx, \izy) arc[start angle={atan2(\izy, \izx)}, delta angle=180, radius=1 cm];
%			\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, delta angle=180, radius=1 cm];
%		\end{scope}
		\begin{scope}[canvas is xy plane at z=0]
			% foreground above s
			\draw (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=180-\stheta, radius=1 cm] coordinate (E);
			% foreground below s
			\draw[dashed] (E) arc[start angle=180-\stheta, end angle={atan2(\izy, \izx)+360}, radius=1 cm] coordinate (F);
			% background below s
			\draw[loosely dotted] (F) arc[start angle={atan2(\izy, \izx)}, end angle=\stheta, radius=1 cm];
			% background above s
			\draw[densely dotted] (-\izx, -\izy) arc[start angle={atan2(-\izy, -\izx)}, end angle=\stheta, radius=1 cm];
		\end{scope}
	\end{tikzpicture}
	\caption{Geometric representation of the element $\ens[e]$ in $A(s)$ with the largest fraction of $\ens[o]$.}
\end{figure}
